RSA Project Report Paper

### 2016-11-29 Paper/Paper.tex
akeem p+1

	\indent A Lucas sequence is a recurrence relation that satisfies of $x^2 - Px+Q$ where with P and Q being integers.In the paper there are seven different identities for Lucas sequences described.These identities stem from this first equation (which is noted by the paper to be the formal definition of a Lucas Sequence)  $U_n(P,Q) = (\alpha^{n}-\beta^{n})/(\alpha-\beta), V_n(P,Q) = \alpha^{n}+\beta^{n}$ where $\alpha$ and $\beta$  are the roots of $x^{}2 - Px+Q$. All the identities won't be outlined here, however there are multiple identities used in the algorithm for the P+1 method. 
	\\\\
	\indent The algorithm itself as outlined in the paper is similar to the following. Let $p = (\prod^{k}_{i=1}q^{\alpha_i}_i - 1)$ where p is a prime factor of N. If we define R in the same way as in the P-1 method then $p+1|R$ and $p|U_R(P,Q)$ thus $p|(U_R(P,Q),N)$. The issues with this method is the calculation of $U_R$ which can be a very large number as the size of R may be very large. A method is described to get around this which ends in an assumption that Q may be set to be equal to one in the calculations of all Lucas sequences involved in this algorithm. 
	\\\\
	\indent There is a second bypass involved to decrease the computational load that leads to the primary implementation done for our assignment. The details to this implementation are outlined in the paper itself. This method was implemented on a laptop computer with a I3 Intel processor that clocks at 2.2 Gigahertz with a RAM size of 4.0 gigabytes. Firstly define a Lucas Sequence to be $V_n = V_{n-1}+V{n_2}$ where $V_0 = 2$ and $V_1 = a$ with a being an integer larger than 2. Then create a loop that continuously calculates $V_{n!}$ where $n \geq 2$. Then after every iteration of this loop calculate the GCD of (N,$V_{n!}-2$) this was done using the Euclid's Algorithm. When the GCD is not equal to either 1 or N, then you have a non trivial factor of N. The major difficulty of implementing this algorithm was the computational overload of calculating subsequent factorial Lucas Sequences. There was a small work around to this to relieve some of the burden of this by recognizing that $V_{n!}(a) = V_n({V_{n-1}})$ meaning if we allow the input to the Lucas sequence to be the output to the previous Lucas Sequence, we can get the factorials of the initial input a without having to actually calculate subsequent factorials of that Lucas Sequence. Without this work around even five iterations of this loop quickly became lengthy to calculate, as it would be $V_120$, an extreme amount of stack calls on the limited hardware being used. The numbers still become prohibitively large for the hardware fairly quickly, in about 15 iterations. So a limit on the number of iterations was engraved in the method (about 15 or so). The paper itself mentions in the implementation and results section that the P+1 method was about 9 times slower than the P-1 method possibly likely due to the calculation of a Lucas sequence on top of the calculation of the factorial that the P-1 method already had. When actually run on the original modulus the algorithm once again found 809 to be a factor about 5 seconds. Use of the method on the modulus with 809 divided out produced no further results, even when run for over 20+ hours. At this time an estimate for the time the program would actually factor the second modulus has not been produced. The only new information that could be extrapolated from this would be that the probability of the p+1 of the larger number being comprised of mostly small factors would be low provided that the premise of the algorithm itself is to be believed. This ends the discussion of William's P+1 method and our attempt to implement it for our assignment.

>>>>

\indent A Lucas sequence is a recurrence relation that satisfies of $x^2 - Px+Q$ where with P and Q being integers.In the paper there are seven different identities for Lucas sequences described.These identities stem from this first equation (which is noted by the paper to be the formal definition of a Lucas Sequence)  $U_n(P,Q) = (\alpha^{n}-\beta^{n})/(\alpha-\beta), V_n(P,Q) = \alpha^{n}+\beta^{n}$ where $\alpha$ and $\beta$  are the roots of $x^{}2 - Px+Q$. All the identities won't be outlined here, however there are multiple identities used in the algorithm for the P+1 method. 
\\\\
\indent The algorithm itself as outlined in the paper is similar to the following. Let $p = (\prod^{k}_{i=1}q^{\alpha_i}_i - 1)$ where p is a prime factor of N. If we define R in the same way as in the P-1 method then $p+1|R$ and $p|U_R(P,Q)$ thus $p|(U_R(P,Q),N)$. The issues with this method is the calculation of $U_R$ which can be a very large number as the size of R may be very large. A method is described to get around this which ends in an assumption that Q may be set to be equal to one in the calculations of all Lucas sequences involved in this algorithm. 
\\\\
\indent There is a second bypass involved to decrease the computational load that leads to the primary implementation done for our assignment. The details to this implementation are outlined in the paper itself. This method was implemented on a laptop computer with a I3 Intel processor that clocks at 2.2 Gigahertz with a RAM size of 4.0 gigabytes. Firstly define a Lucas Sequence to be $V_n = V_{n-1}+V{n_2}$ where $V_0 = 2$ and $V_1 = a$ with a being an integer larger than 2. Then create a loop that continuously calculates $V_{n!}$ where $n \geq 2$. Then after every iteration of this loop calculate the GCD of (N,$V_{n!}-2$) this was done using the Euclid's Algorithm. When the GCD is not equal to either 1 or N, then you have a non trivial factor of N. The major difficulty of implementing this algorithm was the computational overload of calculating subsequent factorial Lucas Sequences. There was a small work around to this to relieve some of the burden of this by recognizing that $V_{n!}(a) = V_n({V_{n-1}})$ meaning if we allow the input to the Lucas sequence to be the output to the previous Lucas Sequence, we can get the factorials of the initial input a without having to actually calculate subsequent factorials of that Lucas Sequence. Without this work around even five iterations of this loop quickly became lengthy to calculate, as it would be $V_120$, an extreme amount of stack calls on the limited hardware being used. The numbers still become prohibitively large for the hardware fairly quickly, in about 15 iterations. So a limit on the number of iterations was engraved in the method (about 15 or so). The paper itself mentions in the implementation and results section that the P+1 method was about 9 times slower than the P-1 method possibly likely due to the calculation of a Lucas sequence on top of the calculation of the factorial that the P-1 method already had. The use of the P+1 method on 50 bit integers produce the factors in an average .0125 to .015 (there were a few outliers that took up to 5-10 seconds however) At around 100 bits the method takes around .5 to .8 seconds to produce a factor. When actually run on the original modulus the algorithm once again found 809 to be a factor in an average time of about .018 to .021 seconds.Despite the results on even some numbers in the 200 bit range(average run time of 2 to 5 seconds)  use on the modulus with 809 divided out produced no further results, even when run for over 20+ hours. The only new information that could be extrapolated from this could be that the probability of the p+1 of the larger number being comprised of mostly small factors would be low provided that the premise of the algorithm itself is to be believed. This ends the discussion of William's P+1 method and our attempt to implement it for our assignment.
